\section{Conclusion}

Sadly, because of time constraints we were only able to meet one optional goal. We planned to include the implementation of a visualization of the transaction DAG as an option. This feature is fully integrated with the project.

However, we also missed some targets we agreed on. We planned to implement a flooding algorithm to allow another option for incentivizing the participation in the system. This feature would have consumed much time and its implementation was halted in in the second half of our implementation time. 

Also, we were not able to test all cases and it is likely that our software has teething problems. However, we are proud to present a working cryptocurrency which is in our tests much faster than Bitcoin. Our weekly meetings improved our teamwork and the ability to understand each others problems and to get a consensus in general.

The current corona situation lowered our productivity in multiple terms: First, we started late with the project part itself. More time for the project implementation and less time for the paper writing would have helped a lot.
Further, we could never set up any meeting in person. Meeting for example in the university would have allowed us to test our system in a real world distributed environment, but would have even been more valuable in the beginning to discuss the theory and design concepts.

Besides the corona related issues, we made the mistake to discuss every single theoretical question as whole group. Everyone was included in most of the theorycrafting at the beginning. It would have helped to just specialize in one specific topic, as originally intended.