\section{Personal Notes}
\paragraph{Nico:} Personally, I have to say that if I were to do this, or any other project group again, I would prefer to do some things different. But before going over those points, I want to admit that I think our project was a success and I would use the product after the teething problems were fixed. I also want to note that I still think that the topic of the paper I worked on in the first half of this project is cool and I am a bit sad that I could not use it in this project. That however leads to the first problem I encountered, time.

If there were more time left, I could have used homomorphic hashing in this project. To tackle this, I would suggest to shorten the time for the theoretical part in the first half. If necessary at all, this time for individual research should be reduced to one third. 

Also, in my personal opinion, is six people not enough to handle a project like this. That is obviously at least partially our own fault, since we set the expectations to met. However, I would have preferred to hear this from our advisors, instead of learning at the "hard way". 

As mentioned above, time and people were two troubling factors for this project. Looking over the target agreement, one will notice that there were points agreed on, which were not fulfilled. For Matthias and my part, this would be the implementation of an alternative option for rewarding Validators. In our project, we agreed to first focus on the other option, since it seemed to be easier to integrate. With other tasks consuming our time and with the late integration of checkpoints into our project, there were no time left to implement the alternative option. This would have needed different network protocols, new application layer logic and a different handling of checkpoints, and could have been probably a different project in itself with the only common factor being the user interface. I think we could have easily handled this part with two more people working on this project, or at least the ability to (safely) meet in person and discuss matters directly and identify problems early.

I was told by some peers, that this is not only my opinion, but I don't want to speak for all.